\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontawesome5}

% Define colors
\definecolor{primary}{RGB}{16, 185, 129} % Emerald
\definecolor{action}{RGB}{59, 130, 246} % Blue
\definecolor{script}{RGB}{55, 65, 81} % Gray
\definecolor{wow}{RGB}{219, 39, 119} % Pink

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary
}

\newtcolorbox{scriptbox}{
    colback=gray!5,
    colframe=gray!40,
    fonttitle=\bfseries,
    title=Script,
    halign=left,
    sharp corners=all,
    boxrule=1pt,
    left=1em,
    right=1em
}

\newtcolorbox{tipbox}{
    colback=yellow!10,
    colframe=yellow!50!black,
    title=\faLightbulb\ Pro-Tip for the Video,
    fonttitle=\bfseries\color{black},
    coltitle=black,
    sharp corners=all,
    boxrule=1pt
}

\begin{document}

\title{\Huge\bfseries \faFilm\ FoodBridge: Official 5-Minute Demo Script \\ \Large (Updated with WOW Features!)}
\date{}
\maketitle
\vspace{-4em}

\noindent
\textbf{Track:} EcoTech \\
\textbf{Platform Location:} \url{http://localhost:5173} \\
\textbf{Preparation:} Open your browser to the local URL, make sure the backend (\texttt{npm run api}) and frontend (\texttt{npm run dev}) are running. Maximize the window.

\vspace{1em}
\hrule
\vspace{1em}

\section*{Phase 1: The Hook \& Landing Page (0:00 – 1:00)}

\noindent\textcolor{action}{\textbf{[ACTION]}} Start recording on the Home Page (\texttt{/}). Scroll smoothly down the page as you talk.

\begin{scriptbox}
"Hello judges! Welcome to \textbf{FoodBridge}, an AI-powered logistics platform engineered to solve the 68 million tonne food waste crisis in India. Our mission is to seamlessly bridge the gap between surplus food generators—like hotels and caterers—and communities in need, in real-time."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll down to the \textit{Live City Pulse Strip}.

\begin{scriptbox}
"Every action on this platform has a tangible environmental impact. Here, you can see our live database feeds computing the exact CO\textsubscript{2} offset in real-time based on the volume of food successfully routed away from landfills."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll past the looping \textit{Real Impact, Real Communities} Photo Gallery to give the judges a professional vibe of food rescue operations. Let it stay on screen for 5 seconds.

\vspace{1em}
\hrule
\vspace{1em}

\section*{Phase 2: The Core Tech - Voice AI \& NLP (1:00 – 2:30)}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll back to top, click the \textbf{Donor} tab. Click the \textbf{Demo Account (donor1)} button to log in instantly.

\begin{scriptbox}
"Let’s look at the Donor perspective. One of the biggest friction points for busy caterers is manual data entry. So, we eliminated it."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Click the \textbf{List Food} button to open the modal. Click the \textbf{\faMicrophone\ Mic icon} and speak: \textit{"We have 15 kilos of cooked rice and dal expiring in 4 hours."} (Or type it manually if you prefer).

\begin{scriptbox}
"Using native Web Speech APIs integrated with our custom Natural Language Processing algorithms, a donor can simply speak. Our NLP engine instantly parses the text, extracting the exact weight, the food category, and calculates the spoilage urgency down to the minute."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Click \textbf{Submit}. \textit{A beautiful slide-up notification component (Toast) will magically appear, notifying success.} Point out the \textbf{\faMagic\ AI Forecast Banner} at the top of the dashboard.

\begin{scriptbox}
"The moment the food is smoothly listed, our temporal forecasting models spring into action, predicting immediate local demand and giving the donor a confidence score for how fast their surplus will be matched."
\end{scriptbox}

\vspace{1em}
\hrule
\vspace{1em}

\section*{Phase 3: The Receiver \& Logistics Flow (2:30 – 3:45)}

\noindent\textcolor{action}{\textbf{[ACTION]}} Click the \textbf{Receiver} button in the Navbar. Click the \textbf{Demo Account (receiver1)} button to log in.

\begin{scriptbox}
"Now, let’s switch to the actual NGO or shelter receiving the food. Here is the Receiver Dashboard."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll down to verify the listing you just created is visible at the top as "SAFE". Point at the Trust Score.

\begin{scriptbox}
"The dashboard immediately ranks available donations. Notice the \textbf{Trust Score}? This is generated by our IsolationForest Anomaly Detection ML model, which flags suspicious or highly perishable donations exceeding safety limits to protect our receivers."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Click \textbf{Accept \& Route} on any listing. Switch to the \textbf{\faMap\ Route View} tab if it doesn't auto-switch. Note how the Map is now alive with sweeping \textbf{Pulse animations} on the markers.

\begin{scriptbox}
"We instantly calculate optimal routing on our live radar map. And when a shelter lacks transport, our automated logistics pipeline takes over..."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll down and click \textbf{Request 3rd-Party Fleet (Dunzo/Porter)}. \\
\noindent\textcolor{wow}{\textbf{[WOW FACTOR!!]}} \textit{A massive burst of Celebration Confetti will coat the screen and a success notification will slide up alongside the WhatsApp simulation.}

\begin{scriptbox}
"...Through external service integrations, we instantly dispatch a third-party fleet like Dunzo or Rapido via automated WhatsApp webhooks—providing zero-friction transport from the donor straight to the shelter."
\end{scriptbox}

\vspace{1em}
\hrule
\vspace{1em}

\section*{Phase 4: Machine Learning \& Admin Control (3:45 – 4:45)}

\noindent\textcolor{action}{\textbf{[ACTION]}} Log out of the Receiver. Click \textbf{Dashboard} in the top right to access the \textbf{Global Command Center (Admin)}. Click on the \textbf{AI Models} tab.

\begin{scriptbox}
"Finally, let's take a look under the hood. As administrators, we have a live diagnostic view of the 8 ML pipelines powering FoodBridge."
\end{scriptbox}

\noindent\textcolor{action}{\textbf{[ACTION]}} Scroll through the charts. Hover over the \textbf{Demand Forecast} chart tooltip.

\begin{scriptbox}
"This is our \textbf{Gradient Boosting Regressor} analyzing historical data to predict 6-hour food demand across different city zones. Alongside it, our Spoilage Risk Engine—trained on thousands of perishable data points with an 82\% accuracy rate—is constantly calculating the exact temporal decay of every active meal."
\end{scriptbox}

\vspace{1em}
\hrule
\vspace{1em}

\section*{Phase 5: The Closing (4:45 – 5:00)}

\noindent\textcolor{action}{\textbf{[ACTION]}} Click the \textbf{Home} button in the top left navbar. Leave the screen on the map.

\begin{scriptbox}
"We've built FoodBridge to be scalable, environmentally critical, and fully automated. We aren't just managing waste—we are engineering a zero-waste future. Thank you!"
\end{scriptbox}

\vspace{2em}

\begin{tipbox}
The new Map Pulses, Toasts, and Confetti will speak volumes to your UX polish! Practice the "List Food" NLP typing/talking sequence and the Confetti triggers a couple of times so your screen recording flows smoothly. You've got this!
\end{tipbox}

\end{document}
